\documentclass[12pt,a4paper,sans]{moderncv}

\moderncvstyle{classic} % style options are 'casual' (default), 'classic', 'banking', 'oldstyle' and 'fancy'
\moderncvcolor{blue}    % color options 'black', 'blue' (default), 'burgundy', 'green', 'grey', 'orange', 'purple' and 'red'

\usepackage[scale=0.85]{geometry}
\setlength{\hintscolumnwidth}{3.8cm} % Adjust width for dates to be in a single line

\name{Arthur de Bona Porton Fernandes}{}
\title{Software Engineer}
\address{Içara -- SC, Brazil}
\phone[mobile]{+55 (48) 99976-9970}
\homepage{arthurbpf.com}
\email{arthurbpfernandes@gmail.com}
\social[linkedin]{arthurbpf}
\social[github]{arthurbpf}

% Set name to a single color
\colorlet{color2}{color1}

\begin{document}

\makecvtitle

\section{Summary}
{I am a software engineer with 6+ years of professional experience.
\
With an interest in technology from a very young age, I've been around computers ever since I can remember. When I first came into contact with programming in my teenage years, I was instantly fascinated. Since then, I have not stopped programming, either for fun or professionally. I found programming to be a valuable skill, and on top of that, it keeps me motivated to deepen my knowledge and push my own limits every day.
\
In 2023, I graduated with a bachelor's degree in computer science. Currently, I'm focusing my studies on the Javascript/Typescript ecosystem, with tools like React, Next.js, React Native, Node.js, Bun, etc.}

\section{Experience}
\cventry{Oct/2025 -- Present}{Lead Software Engineer / Tech Lead}{Monument}{Remote}{}{
  \begin{itemize}
    \item Lead architectural decisions and technical strategy for the development team.
    \item Mentor team members and enforce code quality standards through rigorous reviews and best practices.
    \item Oversee the full software development lifecycle (SDLC), ensuring timely delivery of scalable features.
    \item Drive technical excellence and foster innovation within the engineering culture.
  \end{itemize}
  \bigskip
  Skills: Leadership · Team Mentoring · Software Architecture · NestJS · React · TypeScript · AWS · CI/CD · Code Review
  \bigskip
}

\cventry{Feb/2024 -- Oct/2025}{Software Engineer}{Monument}{Remote}{}{
  \begin{itemize}
    \item Developed and maintained a full-stack application using NestJS and React.
    \item Ensured code quality and reliability by writing comprehensive unit tests with Jest and React Testing Library.
    \item Managed application configuration and data storage using AWS services (SSM, S3).
    \item Built data export services for analytics tools, significantly improving data accessibility.
    \item Engineered performance-optimized dashboards to visualize aggregated data.
    \item Integrated secure payment gateways for efficient transaction processing.
    \item Implemented detailed reporting features to enhance user data insights.
  \end{itemize}
  \bigskip
  Skills: NestJS · Node.js · React · TypeScript · AWS (S3, SSM) · MySQL · Jest · React Testing Library · Git
  \bigskip
}

\cventry{Nov/2020 -- Jan/2024}{Software Engineer}{Useall Software}{Criciúma-SC (Remote)}{}{
  \begin{itemize}
    \item Developed a comprehensive ERP system for electric distribution management using C\# and Ext JS.
    \item Engineered the "Virtual Agency" system serving thousands of end consumers, enabling self-service for critical processes.
    \item Built and maintained the CRM and Commercial systems for customer service and back-office management.
    \item Optimized PL/SQL routines in Oracle Database to improve system performance.
    \item Mentored and trained new team members in technical development and best practices.
  \end{itemize}
  \bigskip
  Skills: .NET Framework · .NET Core · C\# · Ext JS · Oracle Database · PL/SQL · JavaScript · Git
  \bigskip
}

\cventry{07/2019 -- 10/2020}{Progress ABL Engineer}{Agrosys Tecnologia}{Criciúma-SC}{}{
  \begin{itemize}
    \item Developed ERP modules for animal production management using Progress ABL.
    \item Automated complex report generation by consolidating distributed farm data.
    \item Designed and implemented data visualization dashboards.
  \end{itemize}
  \bigskip
  Skills: Progress ABL (4GL) · Linux · JavaScript
  \bigskip
}

\section{Education}
\cventry{2019 -- 2023}{Bachelor's degree in computer science}{UNESC  --  Universidade do Extremo Sul Catarinense}{Criciúma -- SC}{}{}

\cventry{2017 -- 2018 \makebox{(Drop-out)}}{Bachelor's degree in civil engineering}{UNESC  --  Universidade do Extremo Sul Catarinense}{Criciúma -- SC}{}{}

\section{Languages}
\cvitemwithcomment{English}{Advanced}{Can understand and talk about complex subjects without any hindrances. TOEIC score: 950 out of 980 points}
\cvitemwithcomment{Portuguese}{Native}{}

\section{Bootcamps}
\cventry{2021}{GoStack Bootcamp}{Rocketseat}{Online}{}{Bootcamp focused on web applications development, using Node.js, ReactJS and React Native.}

\end{document}
